\documentclass[a4paper,10pt, sans]{moderncv}

%\moderncvtheme[black]{classic}
\moderncvtheme[blue]{classic}

\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{lastpage}

%% Adjust the page margins
\usepackage[scale=0.8,top=1in,bottom=1in]{geometry}
\setlength{\headheight}{15.2pt}
\pagestyle{fancy}
\lhead{ \fancyplain{}{Oriol Colom\'es} }
\rhead{ \fancyplain{}{Curriculum Vitae} }
\cfoot{ \fancyplain{}{\thepage\ of \pageref{LastPage}} }

%% Personal data
\firstname{Oriol}
\familyname{Colomés}% Gené}
%\address{Engelsestraat 73}{2627AA, Delft}{Netherlands}
\title{Curriculum Vitae}
%\phone{858-309-2289}
%\phone{+1 919 660 5200}
%\email{htrnguyen@ucdavis.edu}
\email{j.o.colomesgene@tudelft.nl}
\extrainfo{\url{www.oriolcolomes.com}}
%\extrainfo{\link{http://www.ccom.ucsd.edu/$\sim$hieunt/}}
%\extrainfo{\url{http://www.cs.ucdavis.edu/~hieunt/}}
%\extrainfo{\url{http://www.macs.hw.ac.uk/~hn64/}}

\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}

% the ConTeXt symbol
\def\ConTeXt{%
C%
\kern-.0333emo%
\kern-.0333emn%
\kern-.0667em\TeX%
\kern-.0333emt}
\definecolor{web}{rgb}{0.2,0.2,0.2}
%\definecolor{web}{rgb}{0.5,0.5,0.5}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace{-1cm}
%\section{{Personal statement}}
%I am an early stage investigator and highly motivated to pursue an academic career. The base of the expertise needed to carry out the proposed research began to develop while I was under the mentorship of Prof. Santiago Badia, a leading researcher in the computational mechanics field, at the Universitat Politècnica de Catalunya, with whom I devolped my PhD thesis on “Large scale Finite Element solvers for the large eddy simulation of incompressible turbulent flows”. After completing the PhD I joined Duke University as a Postdoctoral Associate under the supervision of Prof. Guglielmo Scovazzi, where I have been working on different research areas, including stabilized methods for viscoelastoplastic materials,  a-posteriori error estimators for uncertainty propagation and embedded Finite Element methods.

%\section{{Research Interests}}
%\textbf{Development of numerical methods} with emphasis on solving PDEs with the Finite element method, including: Computational fluid dynamics, Computational solid dynamics, Uncertainty Quantification, Turbulence, Large scale computing, Embedded geometries.

\section{{Education}}
\cventry{Mar. 2011 -- Mar. 2016}{\textbf{Ph.D. in Civil Engineering}}{}{}{}{Universitat Polit\`ecnica de Catalunya, Barcelona, Spain 
\newline\hspace*{1em} - Dissertation: \textit{Large scale Finite Element solvers for the large eddy simulation of incompressible turbulent flows}
\newline\hspace*{1em} - Advisor: Santiago Badia} 
\cventry{Sep. 2005 -- Mar. 2011}{\textbf{B.S/M.S. in Civil Engineering}}{}{}{}{Universitat Polit\`ecnica de Catalunya, Barcelona, Spain 
\newline\hspace*{1em} - Final Project: \textit{Footbridge over a railway station in Reus and urban planning of the former cargo area} (in catalan) 
\newline\hspace*{1em} - Advisor: Joan Ramon Casas
\newline\hspace*{1em} - Thesis:  \textit{Damage analysis in impact problems} (in spanish) 
\newline\hspace*{1em} - Advisors: Jose Mu\~noz, Jose Luis Curiel}

\section{{Professional development}}
\cventry{Feb. 2018 -- Mar. 2018}{\textbf{Emerging Leaders Institute program}}{}{}{}{Duke University, Durham, NC, USA}
\cventry{Oct. 2015 -- Jul. 2016}{\textbf{Pg.C. in Innovation and R\&D project management}}{}{}{}{Universitat Oberta de Catalunya, Barcelona, Spain}

\section{{Employment}}
\cventry{Jun. 2020  -- present}{\textbf{Delft University of Technology}}{}{Delft}{Netherlands}{
	{\em Assistant Professor}
	\newline Assistant Professor at the Offshore Engineering Group of the Civil Engineering and Geosciences facutly.}

\cventry{May. 2016  -- May. 2020}{\textbf{Duke University}}{}{Durham}{United States}{
{\em Postoctoral Associate}
\newline Includes software development and research activities within the Computational Modeling Lab in the department of Civil and Environmental Engineering (CEE). Research topics: Uncertainty Quantification, Variational multiscale error estimators, solid dynamics, embedded Finite Element methods. (Advised by Prof. G. Scovazzi)}

\cventry{Apr. 2011  -- Apr. 2016}{\textbf{Centre Internacional de Mètodes Numèrics en Enginyeria}}{}{Castelldefels}{Spain}{
{\em CIMNE fellow and Generalitat de Catalunya fellow}
\newline Includes software development and PhD research activities within the COMFUS group. Research topics: Variational multiscale methods for incompressible turbulent flows. (Supervised by Prof. S. Badia). \\
Teaching assistant from January 2013 to June 2015.}

\section{{Qualification for readership}}
\cventry{Mar. 2019}{\textbf{Lecturer accreditation}}{Catalan University Quality Assurance Agency}{}{Spain}{}


\section{{Awards and Fellowships}}
\cventry{October 2018}{\textbf{Special Doctoral Award}}{}{}{}{Universitat Politècnica de Catalunya}

\cventry{May 2017}{\textbf{Early career travel award for the 14th U.S. National Congress on Computational Mechanics}}{}{}{}{United States Association for Computational Mechanics (USACM)}

\cventry{October 2016}{\textbf{Early career travel award.  SIAM Conference on the Computational Science and Engineering (CSE17)}}{}{}{}{Society for Industrial and Applied Mathematics (SIAM)}

\cventry{Jan. 2013 -- Jan. 2016}{\textbf{FI-DGR doctoral fellowship}}{}{}{}{Generalitat de Catalunya}

\cventry{Apr. 2013 -- May 2013}{\textbf{AAD teaching fellowship}}{}{}{}{Generalitat de Catalunya}

\cventry{Oct. 2009 -- Jun. 2011}{\textbf{Enginycat teaching fellowship}}{}{}{}{Generalitat de Catalunya}


\section{{Teaching experience}}
\cventry{Sep. 2020 -- present}{\textbf{Delft University of Technology}}{Civil Engineering and Geociences}{Delft}{Netherlands}{
	{\em Instructor}
	\newline Includes teaching and preparation of support material for the ``Introduction to Computational Dynamics of Offshore Structures'' course in Offshore and Dredging Engineering master.\\
	(4 ECTS credits)}

\cventry{Jan. 2013 -- Jun. 2015}{\textbf{Universitat Politècnica de Catalunya}}{EETAC}{Castelldefels}{Spain}{
{\em Teaching Assistant (2013/2014) and Instructor (2014/2015)}
\newline Includes teaching and preparation of support material for the ``Structures and Material Strength'' course in Air Navigation Engineering and Airports Engineering degrees.\\
Main lecturer during 2014/2015 course (4.5 ECTS credits)}

\cventry{Oct. 2009 -- Jun. 2011}{\textbf{Universitat Politècnica de Catalunya}}{ETSECCPB}{Barcelona}{Spain}{
	{\em Teaching Assistant}
	\newline Includes practise lectures for the ``Metric Geometry and Representation Systems'' course in Civil Engineering degree.}


\section{{International research projects}}
\cventry{\textbullet}{\textbf{Development of a Robust Numerical Scheme for Modeling Large Strain Deformations of Geological Structures
}}{}{}{}{
	Project funded by ExxonMobil Corporate\\
	Period: 01/01/2016 - 31/12/2019 \\
	Role: Postdoctoral researcher}

\cventry{\textbullet}{\textbf{Uncertainty Quantification in LES Computations of Turbulent Multiphase Combustion in a Scramjet Engine (ScramjetUQ)}}{}{}{}{
Project funded by the US Defense Advance Research Projects Agency (DARPA)\\
Period: 01/01/2016 - 31/12/2018 \\
Role: Postdoctoral researcher}

\cventry{\textbullet}{\textbf{Computational Methods for Fusion Energy (COMFUS)}}{}{}{}{
Starting Grant, Ideas Programme\\
Project funded by the European Research Grant (ERC)\\
Reference: 258443\\
Period: 01/01/2011 - 31/12/2015 \\
Role: Graduate researcher}

\section{{Publications}}

\cvitem{\textbullet}{O. Colom\'es, A. G. Main, L. Nouveau, G. Scovazzi, \textit{A Weighted Shifted Boundary Method for free surface flow problems}, Journal of Computational Physics, Volume 424, January 2021.}

\cvitem{\textbullet}{O. Colom\'es, G. Scovazzi, J. Guilleminot, \textit{On the robustness of Variational Multiscale error estimators for the forward propagation of uncertainty}, Computer Methods in Applied Mechanics and Engineering, Volume 342, December 2018, 384-413.}

\cvitem{\textbullet}{O. Colom\'es, G. Scovazzi, I Sraj, O Knio, O Le Ma\^{i}tre, \textit{A Finite Volume Error Estimator Inspired by the Variational Multiscale Approach}, 2018 AIAA Non-Deterministic Approaches Conference, January 2018, 1178.}

\cvitem{\textbullet}{G. Wang, G. Scovazzi, L. Nouveau, C. E. Kees, S. Rossi, O. Colom\'es, A. Main, \textit{Dual-Scale Galerkin Methods for Darcy Flow}, Journal of Computational Physics, Vol 354, February 2018, 111-134.}

\cvitem{\textbullet}{X. Zeng, G. Scovazzi, N. Abboud, O. Colomés, S. Rossi, \textit{A dynamic variational multiscale method for viscoelasticity using linear tetrahedral elements}, International Journal for Numerical Methods in Engineering, 2017.}

\cvitem{\textbullet}{O. Colom\'es, S. Badia, \textit{Segregated Runge-Kutta time integration of convection-stabilized mixed finite element schemes for wall-unresolved LES of incompressible flows}, Computer Methods in Applied Mechanics and Engineering, Volume 313, January 2017, 189–215.}

\cvitem{\textbullet}{O. Colomés, S. Badia, \textit{Segregated Runge–Kutta methods for the incompressible Navier–Stokes equations}, International Journal for Numerical Methods in Engineering, Vol 105, 8 January 2016, 372-400.}

\cvitem{\textbullet}{O. Colomés, S. Badia, J. Principe, \textit{Mixed finite element methods with convection stabilization for large eddy simulation of incompressible turbulent flows}, Computer Methods in Applied Mechanics and Engineering, Volume 304, June 2016, 294–318.}

\cvitem{\textbullet}{O. Colomés, S. Badia, R. Codina, J. Principe, \textit{Assessment of variational multiscale models for the large eddy simulation of turbulent incompressible flows}, Computer Methods in Applied Mechanics and Engineering, Vol 285, 1 March 2015, 32-63.}


\section{{Papers in preparation or submitted}}

\cvitem{\textbullet}{G. Scovazzi, O. Colom\'es, N. Abboud, D. Valiveti, H. Huang, \textit{A blended transient/quasistatic Lagrangian framework for salt tectonics simulations with stabilized tetrahedral finite elements}, Submitted.}

\cvitem{\textbullet}{M. Lesueur, H. Rattez, O. Colom\'es, \textit{Permeability computation of high resolution µCTscan with an unfitted boundary method to improve accuracy}, Submitted}

\cvitem{\textbullet}{O. Colom\'es, N. Abboud, N. Atallah, D. Valiveti, G. Scovazzi, \textit{Simulating erosion and deposition processes in transient geomechanics: An arbitrary Lagrangian/Eulerian Shifted Boundary framework}, In preparation.}


\section{{Conferences, Workshops and Invited Talks}}

\cvitem{Jul. 2019}{O. Colom\'es, M. khalloufi, A. Main, L. Nouveau, G. Scovazzi, \textit{Embedded Stabilized Methods for Free Surface Flow problems}, US National Conference on Computational Mechanics, Ausitn, Texas, USA}

\cvitem{Apr. 2019}{O. Colom\'es, L. Nouveau, G. Scovazzi, \textit{Embedded Stabilized Methods for Free Surface Flow problems}, FEF 2019, Chicago USA.}

\cvitem{Feb. 2019}{O. Colom\'es, L. Nouveau, G. Scovazzi, \textit{Embedded Stabilized Methods for Free Surface Flow problems}, SIAM-CSE, Spokane, Washington, USA.}

\cvitem{Jul. 2018}{O. Colom\'es, G. Scovazzi, N. Abboud, N. Atallah, \textit{Simulation of Geomechanical Processes Using Viscoelastoplastic Models for Solid Mechanics with Large Deformations}, 13th WCCM, New York, USA.}

\cvitem{Jun. 2018}{O. Colom\'es, G. Geraci, M. S. Eldred and G. Scovazzi, \textit{A Multilevel Monte Carlo approach with an embedded Error Estimator for Computational Fluid Dynamics applications}, ECCM-CFD, Glasgow, UK.}

\cvitem{Apr. 2018}{O. Colom\'es, G. Scovazzi, J. Guilleminot, \textit{On the robustness of Variational Multiscale error estimators for the forward propagation of uncertainty}, SIAM-UQ, Garden Grove, California, USA.}

\cvitem{Jan. 2018}{O. Colom\'es, G. Scovazzi, I Sraj, O Knio, O Le Ma\^{i}tre, \textit{A Finite Volume Error Estimator Inspired by the Variational Multiscale Approach}, AIAA SciTech, Orlando, USA.}

\cvitem{Aug. 2017}{O. Colom\'es, \textit{The Variational Multiscale method: from stabilization to uncertainty quantification}, Applied Mathematics Colloquium, UNC, Chapel Hill, USA}

\cvitem{Jul. 2017}{O. Colomés, G. Scovazzi \textit{Variational Multiscale Error Estimators for the Uncertainty Quantification of Mesh Discretization Errors}. US National Conference on Computational Mechanics, Montreal, Canada}

\cvitem{Jul. 2017}{O. Colomés, S. Badia \textit{Extremely scalable Finite Element solvers for turbulent incompressible flows through segregated Runge-Kutta schemes}. SIAM Anual Meeting, Pittsburgh, USA}

\cvitem{Mar. 2017}{O. Colomés, G. Scovazzi \textit{Mesh discretization error and uncertainty quantification: a variational multiscale approach}. USACM Uncertainty Quantification and Data-Driven Modelling workshop, Austin, USA.}

\cvitem{Feb. 2017}{O. Colomés, G. Scovazzi \textit{Mesh discretization error and uncertainty quantification: a variational multiscale approach}. SIAM Conference on Computational Science and Engineering, Atlanta, USA.}

\cvitem{May 2015}{S. Badia, O. Colomés, P. Kus, A. Martin, M. Olm, J. Principe. \textit{On a scalable multiscale/multiphysics finite element framework}. VI International Conference on Computational Methods for Coupled Problems in Science and Engineering, Venice, Italy.}

\cvitem{Apr. 2015}{S. Badia, O. Colomés, P. Kus, A. Martin, M. Olm, J. Principe. \textit{FEMPAR: A scalable multiphysics finite element framework}. 1st Pan-American Congress on Computational Mechanics, Buenos Aires, Argentina.}

\cvitem{Mar. 2015}{S. Badia and O. Colomés. \textit{Segregated Runge-Kutta time integrators for large scale simulations of turbulent incompressible Flows}. SIAM Conference on Computational Science and Engineering, Salt Lake City, USA.}

\cvitem{Jul. 2014}{O. Colom\'es, S. Badia, R. Codina and J. Principe. \textit{Variational multiscale large eddy simulation of turbulent incompressible flows}. 11th World Congress on Computational Mechanics, Barcelona, Spain.}

\cvitem{Oct. 2013}{O. Colom\'es, S. Badia, R. Codina and J. Principe. \textit{Variational multiscale large eddy simulation of turbulent incompressible flows}. 7th workshop on research in turbulence and transition, Terrassa, Spain.}

\cvitem{Nov. 2013}{S. Badia, R. Codina, O. Colom\'es and J. Principe. \textit{Variational multiscale Large Eddy Simulation of turbulent incompressible flows}. VMS 2013, Barcelona, Spain.}

\cvitem{Feb. 2013}{J. Principe, S. Badia, R. Codina and O. Colom\'es. \textit{Dynamic nonlinear variational multiscale modelling of turbulent flows}.  Advances in Computational Mechanics, San Diego, California USA.}

\cvitem{Sep. 2012}{S. Badia, O. Colomés, A. Martin, J. Principe. \textit{Substructuring domain decomposition algorithms for parallel 3D fluid-structure interaction simulations}, ECCOMAS 2012, Vienna, Austria.}


\section{{Reviewer in international Journals}}
\cvitem{\textbullet}{\textbf{Journal of Computational Physics}, Elsevier}
\cvitem{\textbullet}{\textbf{International Journal for Numerical Methods in Fluids}, Wiley}
\cvitem{\textbullet}{\textbf{Computers and Fluids}, Elsevier}


\section{{Academic societies}}
\cvitem{\textbullet}{\textbf{Society for Industrial Applied Mathematics (SIAM)}, US}
\cvitem{\textbullet}{\textbf{US Association for Computational Mechanics (USACM)}, US}
\cvitem{\textbullet}{\textbf{Sociedad Española de M\'etodos Num\'ericos en Ingenieria (SEMNI)}, Spain}


\section{{Patents}}
\cvitem{}{J. Castellón, O. Colomés. 2013. \textit{Pre-fabricated structural element}. PCT/ES2014/070320, filed April 16, 2014, and issued December 11, 2014.}


%\section{\textbf{Computer Skills}} 
%\cvitem{}{$ \bullet $ Operating Systems: Unix/Linux, Windows, Mac OS.}
%\cvitem{}{$ \bullet $ Languages:
%\newline\hspace*{0.5cm} - Advanced: Fortran (95/2003), Python, Matlab, Latex.
%\newline\hspace*{0.5cm} - Basic : C++,Java, HTML.}
%\cvitem{}{$ \bullet $ Experienced in programming:
%\newline\hspace*{0.5cm} - Finite Element Method.
%\newline\hspace*{0.5cm} - Navier-Stokes equations.
%\newline\hspace*{0.5cm} - Parallel applications with MPI, OpenMPI.}
%\cvitem{}{$ \bullet $ Experience in software:
%\newline\hspace*{0.5cm} - Engineering software: GiD, Abaqus, Castem, Autocad, SAP2000.
%\newline\hspace*{0.5cm} - Mathematical software: Matlab, Microsoft Excel.}


%\section{{References}}
%\cvitem{}{\textbf{Prof. Santiago Badia}
%\newline{\em e-mail:} santiago.badia@monash.edu}
%%\newline{\em Phone:} (+34) 934134108}
%
%\cvitem{}{\textbf{Prof. Guglielmo Scovazzi}
%\newline{\em e-mail:} guglielmo.scovazzi@duke.edu}

%\cvitem{}{\textbf{Prof. Omar Knio}
%\newline{\em e-mail:} omar.knio@kaust.edu}

%\cvitem{}{\textbf{Dr. Javier Principe}
%\newline{\em E-mail:} principe@cimne.upc.edu
%\newline{\em Phone:} (+34) 934134182}
%
%\cvitem{}{\textbf{Dr. Ramon Codina}
%\newline{\em E-mail:} ramon.codina@upc.edu
%\newline{\em Phone:} (+34) 934016486}

\vspace*{\fill}
Latest update: \today


\end{document}
